Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-15 nips_2018.tex
First geom stuff insertion

 \section{Contribution and Outlook}
We contribute an algorithm, \systemEnding, that learns to program by bootstrapping a DSL with new
domain-specific primitives that the algorithm itself discovers,
together with a neural recognition model that learns how to
efficiently deploy the DSL on new tasks. We believe this integration
of top-down symbolic representations and bottom-up neural networks --
both of them learned -- could help make program induction systems more
generally useful for AI. Many directions remain open. Two immediate
goals 
are to integrate more sophisticated neural recognition
models~\cite{devlin2017robustfill} and program
synthesizers~\cite{solar2008program}, which may improve performance in
some domains over the generic methods used here.
Another direction is to
explore DSL meta-learning: Can we find a \emph{single} universal
primitive set that could effectively bootstrap DSLs for new domains,
including the four domains considered,  but also many others?

>>>>

 \section{Contribution and Outlook}

\begin{wrapfigure}{r}{0.4\textwidth}
  \begin{center}
    \includegraphics[width = 0.4\textwidth]{figures/geomCompiled.eps} 
  \end{center}
  \caption{
  Future: dreams.
  Top left: hand crafted traning targets. Top right: examples of
  discovered compiled new programs. Bottom: compiled programm across iterations
  to highlight structure emergence.
  }\label{geomCompiled} 
\end{wrapfigure}

We contribute an algorithm, \systemEnding, that learns to program by bootstrapping a DSL with new
domain-specific primitives that the algorithm itself discovers,
together with a neural recognition model that learns how to
efficiently deploy the DSL on new tasks. We believe this integration
of top-down symbolic representations and bottom-up neural networks --
both of them learned -- could help make program induction systems more
generally useful for AI. Many directions remain open. Two immediate
goals 
are to integrate more sophisticated neural recognition
models~\cite{devlin2017robustfill} and program
synthesizers~\cite{solar2008program}, which may improve performance in
some domains over the generic methods used here.
Another direction is to
explore DSL meta-learning: Can we find a \emph{single} universal
primitive set that could effectively bootstrap DSLs for new domains,
including the four domains considered,  but also many others?
